Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-07-30 paper/main.tex
Some slight restructuring. Next: time to think about the evaluation.

\section{Overview}

\emph{(Data pipeline summary)} Our raw data consist of every Python 3 program
that a user executed on PythonTutor.com (not in "live" mode) during 2017, other
than those with syntax errors or undefined variables. Each program which crashes
(throws an uncaught Python exception) is paired with
the next program (by the same user) that does not crash, under the assumption
that the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a stddev
above average), since these are most likely to be violations of that
assumption (i.e. the program that does not crash is unrelated to the crashing
program).

For each statement and expression in each
program, we compute features including the following:

@@

Each vector is then one-hot encoded (e.g. feature "Type : Int" becomes set
of features "Type-Int : 1", "Type-Bool : 0", "Type-Str : 0", etc.) for use with
standard machine learning tools. The models we train (inc. decision trees/forests,
MLP, GBM) can then rank expressions of a test program in order of how likely they
are to be the source of the bug, so we can compute Top-k accuracies: how often
is the true program change located in the model's first k outputs. We report Top-1
and Top-3...

\section{Approach}

\section{Evaluation}

@@

>>>>

\section{Overview and Approach}

We present an algorithm for accurately localizing faults~\cite{tarantula} in
dynamically-typed Python programs that exhibit non-trivial uncaught runtime
exceptions. We do not consider syntax errors or references to undefined
variables. Our algorithm uses machine learning models based on static and
dynamic features to implicate suspicious expressions. Since studies have
found that voluminous fault localization output is not useful to
developers~\cite{orso-parnin,orso-parnin2013}, we focus on producing
Top-1 and Top-3 rankings.

Our algorithm first extracts static and dynamic features from Python
program (Section~\ref{sec-features}). Next, using a labeled training
corpus, we learn a machine learning model over those features
(Section~\ref{sec-model}). Once the model has been learned, we localize
faults in new Python programs by extracting their features and applying the
model.

\subsection{Feature Extraction}
\label{sec-features}

Our key insight is that FIXME-INSIGHT. Are a result, we make use of
static, dynamic and contextual information. Static features, such as FIXME,
are effective at capturing FIXME-INFORMATION. By contrast, dynamic
features, such as FIXME, support the modeling of FIXME. Finally, we also
include contextual information, such as FIXME, which allows our algorithm
to accurately handle FIXME. We consider the empirical justification of
these features in Section~\ref{sec-eval}.

We calculate features for each statement and expression in the program.

@@

Each vector is then one-hot encoded (e.g. feature "Type : Int" becomes set
of features "Type-Int : 1", "Type-Bool : 0", "Type-Str : 0", etc.) for use with
standard machine learning tools.

\subsection{Machine Learning and Modeling}
\label{sec-model}

The models we train (inc. decision trees/forests,
MLP, GBM) can then rank expressions of a test program in order of how likely they
are to be the source of the bug, so we can compute Top-k accuracies: how often
is the true program change located in the model's first k outputs.

\section{Evaluation}
\label{sec-eval}

We conducted a large-scale empirical evaluation of our algorithm with the
aim of addressing a number of research questions: 
\begin{enumerate}

\item[RQ1]{Can we accurately localize non-trivial faults in Python
programs?}

\item[RQ2]{Which features are the most important for Python fault
localization?}

\item[RQ3]{FIXME}

\end{enumerate}

\subsection{Data Set}

Our raw data consist of every Python 3 program that a user executed on
PythonTutor.com~\cite{Guo2013-vu} (not in ``live'' mode) during 2017, other
than those with syntax errors or undefined variables.  Each program which
crashes (throws an uncaught Python exception) is paired with the next
program (by the same user) that does not crash, under the assumption that
the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a
stddev above average), since these are most likely to be violations of that
assumption (i.e., the program that does not crash is unrelated to the
crashing program).

In our evaluation, we used FIXME as a training set and FIXME as a held-out
evaluation set. We employed cross-validation~\cite{kohavi} to help address
the potential threat of overfitting.

@@

For these evaluations, we employ machine learning algorithm FIXME, which
provided the best balance of FIXME and FIXME (time? accuracy?) on our
training set.

We report Top-1 and Top-3...

We define FIXME-ACCURACY to be FIXME.

\subsection{RQ 1 --- Fault Localization Accuracy}
\subsection{RQ 2 --- Feature Predictive Power}
\subsection{RQ 3 --- FIXME}
